Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-31 TACAS2018/paper.tex
wording

Next, we are interested in studying models with parametric inputs, which are
described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
is computed next.
%
\begin{lemma}
%
The state of the model
$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a
parametric input $\vec{u}$ is
%
\begin{align}
\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
\label{eq:continuous_tube_param}
\end{align}
%
where $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
\eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,
we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}. 
If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
$A_d=e^{\mat{A} T_d}$, then
$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u})
\text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} =
e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the
system at time $T$.
%
\end{lemma}

@@

The final case we analyze is that of hybrid-time models, where the plant
dynamics evolve in continuous time while the feedback dynamics evolve in
discrete time.  A new input value is produced only at every sample time but
implemented over the continuous-time plant dynamics.
%
\begin{theorem}
The expression
 \begin{align}
 \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
 \label{eq:cyber_feedback}
 \end{align}
 with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in \eqref{eq:continuous_tube_param}, 
 and $\mat{A}_d=\mat{A}_{T_s}, \mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with sample time $T_s$, 
 is the state of the model 
 \begin{align*}
 \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
 \vec{u}(t)=\mat{K}\vec{x}_k,  \,
 kT_s \leq t < (k+1)T_s. 
 \end{align*}
 For the proof see Appendix~\ref{sec:proofs}
 \end{theorem}
%\begin{proof}
%See Appendix~\ref{sec:proofs}
%\end{proof}

@@

In our model, delays are all deferred to the Zero Order Holder (ZOH) of the
DAC (See Figure \ref{fig:observersystem}).  In the digital world everything
takes place at times $t=kT_s, k \in \mathbb{N}$ (discrete time progression),
and the output signal is delayed at the DAC when fed back to the
continuous-time domain at time ($t=kT_s+t_d$).

\begin{theorem}
The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modeled as a non-deterministic disturbance signal ($\nu_t$ in Figure \ref{fig:observersystem}) upper bounded by 
\begin{align}
\norm{\vec{y}_{k}-{\vec{y}_{t_d}}_{k}}_1 \leq q_t, \text{ where } q_t=&(\norm{\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})}_1+\norm{\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}}_1)\norm{U}_1
\end{align}
where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, $t_s=T_s-t_d$,
and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm, 
which we extend to sets as $\norm{X}_1 = \sup \{\norm{\vec{x}}_1, \vec{x} \in X\}$.  
For the proof see Appendix~\ref{sec:proofs}
\end{theorem}
%
%\begin{proof}
%See Appendix~\ref{sec:proofs}
%\end{proof}
This result allows to over-approximate the effects of the delay by introducing a disturbance signal $\nu_t=[-q_t, q_t]$ at the output.
 %and use the dynamics of the system without delay.  
 This noise will be small when the delay is much smaller than the sampling time ($t_s\approx T_s$ and $\mat{B}_{t_d} \approx 0$).

>>>>

Next, we are interested in studying models with parametric inputs, which are
described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
is computed next.
%
\begin{lemma}
%
The state of the model
$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a
parametric input $\vec{u}$ is
%
\begin{align}
\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
\label{eq:continuous_tube_param}
\end{align}
%
where $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
\eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,
we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}. 
If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
$A_d=e^{\mat{A} T_d}$, then
$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u})
\text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} =
e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the
system at time $T$.
%
\end{lemma}

@@

The final case we analyze is that of hybrid-time models, where the plant
dynamics evolve in continuous time while the feedback dynamics evolve in
discrete time.  A~new input value is produced only at every sample time but
implemented over the continuous-time plant dynamics.
%
\begin{theorem}
The expression
%
 \begin{align}
 \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
 \label{eq:cyber_feedback}
 \end{align}
%
with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s},
\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
sample time $T_s$, is the state of the model
%
\begin{align*}
 \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
 \vec{u}(t)=\mat{K}\vec{x}_k,  \,
 kT_s \leq t < (k+1)T_s \,. 
\end{align*}
%
For the proof see Appendix~\ref{sec:proofs}
%
\end{theorem}
%\begin{proof}
%See Appendix~\ref{sec:proofs}
%\end{proof}

@@

In our model, delays are all deferred to the Zero Order Holder (ZOH) of the
DAC (See Figure \ref{fig:observersystem}).  In the digital world everything
takes place at times $t=kT_s$ for $k \in \mathbb{N}$ (discrete time
progression), and the output signal is delayed at the DAC when fed back to
the continuous-time domain at time ($t=kT_s+t_d$).

\begin{theorem}
%
The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a
discrete feedback controller for a continuous LTI system can be modeled as a
non-deterministic disturbance signal ($\nu_t$ in
Figure~\ref{fig:observersystem}) upper bounded by
%
\begin{align}
\norm{\vec{y}_{k}-{\vec{y}_{t_d}}_{k}}_1 \leq q_t, \text{ where } q_t=&(\norm{\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})}_1+\norm{\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}}_1)\norm{U}_1
\end{align}
where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, $t_s=T_s-t_d$,
and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm, 
which we extend to sets as $\norm{X}_1 = \sup \{\norm{\vec{x}}_1, \vec{x} \in X\}$.  
For the proof see Appendix~\ref{sec:proofs}
\end{theorem}
%
%\begin{proof}
%See Appendix~\ref{sec:proofs}
%\end{proof}
This result allows to over-approximate the effects of the delay by introducing a disturbance signal $\nu_t=[-q_t, q_t]$ at the output.
 %and use the dynamics of the system without delay.  
 This noise will be small when the delay is much smaller than the sampling time ($t_s\approx T_s$ and $\mat{B}_{t_d} \approx 0$).
